|

### 2023-05-03 paper.Rmd
model mispecifcation description not quite right -> reworked

Model misspecification occurs if functions of predictors that needed to accurately describe the relationship between response and predictors are omitted. Any non-linear pattern visible in the residual plot could be indicative of this problem. An example residual plot containing visual pattern of non-linearity is shown in Figure \ref{fig:residual-plot-common-departures}B. One can clearly observe the "S-shape" from the residual plot, which corresponds to cubic term that should have been included in the model.

>>>>

Model misspecification occurs if functions of predictors that needed to accurately describe the relationship with the response are incorrectly specified. This includes instances where a higher-order polynomial term of a predictor is wrongfully omitted. Any non-linear pattern visible in the residual plot could be indicative of this problem. An example residual plot containing visual pattern of non-linearity is shown in Figure \ref{fig:residual-plot-common-departures}B. One can clearly observe the "S-shape" from the residual plot, which corresponds to cubic term that should have been included in the model.
